Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding subsection separators.
Try to make a better case against code blocks

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt containers} package.

\begin{quote}
\small
\begin{verbatim}
-- | /O(1)/. Is the map empty?
--
-- > Data.Map.null (empty)           == True
-- > Data.Map.null (singleton 1 'a') == False

null :: Map k a -> Bool
null Tip      = True
null (Bin {}) = False
\end{verbatim}
\end{quote}

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.

\begin{quote}
    \emph{sol: I think the Haddock comment only contains properties.
    So the argumentation is shaky?} \\
    \emph{kazu: My point is that we cannot tell which the author of packages
   want to express, examples or properties.}
\end{quote}

If the equations above are examples, we cannot distinguish
their results from their expression to be evaluated.
If they are properties, they should be distinguished
from example code.

@@

\subsection{Reusable spec}

@@

\subsection{Source locations for failing examples}

@@

\subsection{TBD}

>>>>

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt filepath} package.

\begin{quote}
\small
\begin{verbatim}
-- | Does the given filename have an extension?
--
-- > null (takeExtension x) == not (hasExtension x)
hasExtension :: FilePath -> Bool
hasExtension = any isExtSeparator . takeFileName
\end{verbatim}
\end{quote}

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.  The code
block contains a property.  And it would be useful to have a tool that
automatically extracts and tests the property.
But writing such a tool is hard, because it is not easy to decide if
the code block is a property, an example, or some random code snippet.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reusable spec}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Source locations for failing examples}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TBD}
